|

### 2023-04-28 manuscript/Chapter2-appendix1.Rmd
update appendix 1

```{r figS3, out.width = "100%", fig.cap = "**Figure S3.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM. The test is displayed on the y axis (i.e. whether the group of interest has either a greater or smaller value), and the parameter value is displayed on the x axis. Each panel represent the experience level groups that are being compared."}

@@

```{r figS4, out.width = "80%", fig.cap = "**Figure S4.** Posterior median differences and 95% credible intervals in the correlations of players when they were advanced vs novice. The difference is displayed on the x axis and the parameter correlations are displayed on the y axis."}

>>>>

```{r figS3, out.width = "100%", fig.cap = "**Figure S3.** Posterior median differences and credible intervals comparing the parameter values predicted by the MDHGLM between each predator experience level. Each panel represent the experience levels that are compared. The parameter being compared is displayed on the y axis (e.g. whether the standard deviation of predator ID on the mean differs when the population was intermediate vs novice), and the difference is displayed on the x axis."}

@@

```{r figS4, out.width = "80%", fig.cap = "**Figure S4.** Posterior median differences and credible intervals comparing the correlations between traits when predators were advanced vs novice. The median difference is displayed on the x axis and the trait correlations being compared are displayed on the y axis."}
